\Large \bf \projtitle

### 2015-05-05 doc/paper/paper.tex
deleting duplicated code
Write implementation section

\usepackage{style, verbatim, url, graphicx}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{cleveref, breakurl}

@@

\newcommand{\zbf}{Zauberfl\"{o}te}
\newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=.8\linewidth]{components.eps}
        \caption{Relationship between different components of the \zbf
        peer-to-peer download service.}
        \label{fig:components}
    \end{centering}
\end{figure}

>>>>

\usepackage{style, verbatim, url, graphicx}
\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{caption}
\usepackage{cleveref, breakurl}

@@

\newcommand{\zbf}{Zauberfl\"{o}te}
\newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
\newcommand{\inclfigure}[3]{
    \begin{figure}
        \begin{centering}
            \includegraphics[width=.8\linewidth]{#2}
            \caption{#3}
            \label{#1}
        \end{centering}
    \end{figure}
}

@@

The \zbf\ architecture consists of several loosely-connected components (see
figure~\ref{fig:components}). At the highest level, there is a download manager that
provides a reliable download service. It relies on the tracker interface and
the connection manager. The tracker interface facilitates communication with
the central tracker for information about peers and file sizes, and the
connection manager provides an interface for peer-to-peer message transfer.

Our components rely on two standard APIs provided by modern browsers,
WebSockets~\cite{w3c:websocket} for client-server communication and
WebRTC~\cite{w3c:webrtc} for peer-to-peer communication.

\inclfigure{fig:components}{components.eps}{
    Relationship between different components of the \zbf\ peer-to-peer
    download service. Components in gray are standard browser APIs.
}
